Truthfulness Verification System

### 2011-05-04 trunk/proposal/paper.tex
alg 1 description added

\subsection{Bag of words}

>>>>

\subsection{Bag of words}
In the bag of words method, we are exploiting the fact that for true sentence we will have high content word match between pages obtained from topic unit and alternate units. Overall steps of this method are described below:
\begin{itemize}
\item For all possible k-grams $(k=1,2,3,...,topic\_unit\_length)$ of topic unit we find relevant wikipedia page using wikipedia search API. Although it may seems that taking all possible k-grams will introduce noise in the retrieved data, this is not the case because there will be no pages for irrelevant k-gram consisting of irrelevant combination of words. Now for each possible k-gram we may get a Wikipedia page directly or we may go need to disambiguate if that k-gram refers to multiple possible pages in Wikipedia. If we get a single page without any ambiguation then we take that page. However, if we need to disambiguate then we look into all possible wikipedia pages and disambiguate them using highest intersection of words of topic unit and description of the wikipedia page for the disambiguation link. Here we take all words except the k-gram for which we are disambiguating as a set of words for intersection. So assume that at the end of this step we get $n$ wikipedia pages either directly or through disambiguation.

\item Now for each of the five alternative units generated by the T-verifier we also find a wikipedia page. Here also we may get a Wikipedia page directly or we may need to disambiguate if there are multiple possible pages. If we need disambiguation then we disambiguate using same approach described previously i.e. maximal intersection of words between the description of disambiguation link and words of topic unit.

\item We have five Wikipedia pages for each of the alternative units now and $n$ pages from topic unit. We generate bag of words i.e. content words for all the five pages for alternate units and $n$ pages for topic unit.

\item Now for each of the page corresponding to alternate units we count intersection of words for each $n$ pages for topic unit and take sum of  intersection count for an alternate unit page and $n$ topic unit page. Hence at this step we have a count value associated with each of the alternate unit and we rank all the alternate units according to this value to produce truth confidence or rank for all five alternate units.
\end{itemize}
